\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-03-27 paper.tex
Update quarto and rendered

\section{Introduction}\label{sec-intro}

\begin{itemize}
\tightlist
\item
  What's the problem
\item
  Summary of literature
\end{itemize}

>>>>

\begin{itemize}
\tightlist
\item
  What's the problem:
\end{itemize}

Non-linear dimension reduction being used to summarise high-dimensional
data.

\begin{itemize}
\tightlist
\item
  Summary of literature
\end{itemize}

Relevant high-d vis, NLDR history

\begin{figure}[H]

\centering{

\includegraphics{paper_files/figure-pdf/fig-umapauthor-1.pdf}

}

\caption{\label{fig-umapauthor}2D layout from UMAP (n\_neighbors = 30,
min\_dist = 0.3) applied for the PBMC3k dataset. Is this a best
representation of the original data?}

\end{figure}%
